### 2017-06-18 src/algorithm.tex
alg

Let $O(v_v, v_p)$ denote the optimal embedding of a $s_vv_v$-path into a
$s_pv_p$-path.
Let $pi:V_v \to \N$ be any typological ordering of $V_v$. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&O(v_v, v_p) = 
\min_{\substack{
u_v : pi(u_v) < pi(v_v), 
\\
u_pv_p \in A_p
}}
O(u_v, u_p)
+
\argmin_{C : T_{v_p}(u_v, v_v, C) \leq p_c(v_p)}
\\
&O(s_v, v_p) = c(s_v, v_p)
\end{align*}

>>>>

Let $O(v_v, v_p)$ denote the optimal embedding of a $s_vv_v$-path into a
$s_pv_p$-path.
Let $pi:V_v \to \N$ be any typological ordering of $V_v$. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&O(v_v, v_p) = 
\min_{\substack{
u_v : pi(u_v) \leq pi(v_v), 
\\
u_pv_p \in A_p
}}
O(u_v, u_p)
+
\argmin_{C : T_{v_p}(u_v, v_v, C) \leq p_c(v_p)}
\\
&O(s_v, v_p) = c(s_v, v_p)
\end{align*}

\begin{figure}[ht]
\centering
\input{fig-dp1}
\caption[]{
The optimal embedding of a $s_vw_v$-path into a $s_pw_p$ path can be efficiently 
computed by breaking the problem into the problem of embedding a $s_vu_v$-path
into a $s_pv_p$-path (blue, dashed rectangles) 
and the problem of embedding a $u_vw_v$-path into $w_p$ (red, dotted
rectangles) where $b_d(u_v, v_v) \leq b_c(v_p, w_p)$.
}
\end{figure}
